A Model for Extracting Time Delays from Noisy Time Series Data

### 2013-08-20 doc/Paper1/ms.tex
ell is a good letter

\begin{table*}
\begin{tabular}{lll}
\hline
{\bf Parameter} &	{\bf Meaning}			& {\bf Prior}\\
\hline
$\tau_2$	&	Time delay relative to image 1	& Cauchy()$T(,)$\\
$\{m_1, m_2\}$	&	Mean magnitude for each image	& Uniform()\\
\hline
{\bf Data}	&	{\bf Meaning}			& {\bf Sampling Distribution}\\
\hline
$\{Y_1, ..., Y_N\}$ &	Noisy magnitude measurements	& $\mathcal{N}\left(\mathbf{m}(\params), \mathbf{C}(\params)\right)$\\
\hline
{\bf Prior Information} & {\bf Meaning}			&\\
\hline
$N$		&	Number of measurements (all images together)\\
$\{t_1, ..., t_N\}$ &	Measurement times\\
$\{k_1, ..., k_N\}$ &	Flags identifying which image was observed
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\begin{tabular}{lll}
\hline
{\bf Parameter} &	{\bf Meaning}			& {\bf Prior}\\
\hline
$\tau_2$	&	Time delay relative to image 1	& Cauchy()$T(,)$\\
$\{m_1, m_2\}$	&	Mean magnitude for each image	& Uniform()\\
$L$		&	Length scale of QSO variations	& LogUniform()\\
$\{\ell_1, \ell_2\}$ &	Length scale of image-specific variations & \\
\hline
{\bf Data}	&	{\bf Meaning}			& {\bf Sampling Distribution}\\
\hline
$\{Y_1, ..., Y_N\}$ &	Noisy magnitude measurements	& $\mathcal{N}\left(\mathbf{m}(\params), \mathbf{C}(\params)\right)$\\
\hline
{\bf Prior Information} & {\bf Meaning}			&\\
\hline
$N$		&	Number of measurements (all images together)\\
$\{t_1, ..., t_N\}$ &	Measurement times\\
$\{k_1, ..., k_N\}$ &	Flags identifying which image was observed
\end{tabular}
\end{table*}
